### 2023-09-20 paper.tex
fixed one more typo

In Figure 2, we split the sample by the median founding year vacancy rate (the cutoff is 3.94\%), and plot the kernel density of local wage across above-median (high) revenue sellers and below-median (low) revenue sellers for each subsample. The threshold between high and low revenue seller for log quarterly revenue is 4.64. The left panel shows that when low vacancy rate is low, the relative proportion of sellers that end up with high (low) revenues decreases (increases) in local wage in the founding year. In the right panel, the difference in the distribution in founding year local wages between high and low revenue sellers is much smaller.

>>>>

In Figure 2, we split the sample by the median founding year vacancy rate (the cutoff is 3.94\%), and plot the kernel density of local wage across above-median (high) revenue sellers and below-median (low) revenue sellers for each subsample. The threshold between high and low revenue seller for log quarterly revenue is 4.64. The left panel shows that when vacancy rate is low, the relative proportion of sellers that end up with high (low) revenues decreases (increases) in local wage in the founding year. In the right panel, the difference in the distribution in founding year local wages between high and low revenue sellers is much smaller.
